---
title: "iteraction_listcols"
output:   
  github_document
---

site_libs for HW4 potential answer on discussion board

Data frames are basically a special kind of list.
- Can use list column into data frame which differing types of variables

### Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
set.seed(1)
```

## List
```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, FALSE, TRUE, TRUE)
```

Let's look at a list
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix (1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000))
)
```

Accessing list items
```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```


## Loops!
Let's write a for loop to take mean and SD of four samples from a normal distribution
```{r}
list_norm <- 
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, 0.4),
    d = rnorm(20, 100, 1)
  )
```

Here's my function

```{r}
mean_and_sd <- function(x){
  if(!is.numeric(x)){
    stop("Mean and SD only work for numbers")
  }
  
  if (length(x) < 3){
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Let's try to make this work
```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])

```

Let's use a `for` loop instead
```{r}
output <- vector("list", length = 4)

for (i in 1:4){
  
  output[[i]] = mean_and_sd(list_norm[[i]])

}
```

## Map!!

```{r}
map(list_norm, mean_and_sd)
```

so... what about other functions?

```{r}
map(list_norm, median)
map(list_norm, var)
map(list_norm, summary)
```

map variants...
```{r}
map_dbl(list_norm, median)

map_df(list_norm, mean_and_sd)
```






