---
title: "iteraction_listcols"
output:   
  github_document
---

site_libs for HW4 potential answer on discussion board

Data frames are basically a special kind of list.
- Can use list column into data frame which differing types of variables

### Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)
set.seed(1)
```

## List
```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, FALSE, TRUE, TRUE)
```

Let's look at a list
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix (1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000))
)
```

Accessing list items
```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```


## Loops!
Let's write a for loop to take mean and SD of four samples from a normal distribution
```{r}
list_norm <- 
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, 0.4),
    d = rnorm(20, 100, 1)
  )
```

Here's my function

```{r}
mean_and_sd <- function(x){
  if(!is.numeric(x)){
    stop("Mean and SD only work for numbers")
  }
  
  if (length(x) < 3){
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Let's try to make this work
```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])

```

Let's use a `for` loop instead
```{r}
output <- vector("list", length = 4)

for (i in 1:4){
  
  output[[i]] = mean_and_sd(list_norm[[i]])

}
```

## Map!!
Helps make code readable

```{r}
map(list_norm, mean_and_sd)
```

so... what about other functions?

```{r}
map(list_norm, median)
map(list_norm, var)
map(list_norm, summary)
```

map variants...
```{r}
map_dbl(list_norm, median)

map_df(list_norm, mean_and_sd)
```

## list columns...

```{r}
listcol_df <-
  tibble(
    name = c("a", "b", "c", "d"),
    norm = list_norm
  )

listcol_df[["norm"]]

output <- map(listcol_df[["norm"]], mean_and_sd)
```

can we add list columns and then what
```{r}
listcol_df %>%
  mutate(
    m_sd = map(norm, mean_and_sd)
  ) %>%
  select(-norm)
```

## What about something more realistic...

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's nest within weather stations...
```{r}
weather_nest_df <-
  weather_df %>%
  nest(data = date:tmin)
```

Really is a list column!

```{r}
weather_nest_df[["data"]]
```

```{r}
weather_nest_df[["data"]][[1]] # df within df

lm(tmax ~ tmin, data = weather_nest_df [["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest_df [["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest_df [["data"]][[3]])
```

Let's write a short lil function

```{r}
weather_lm = function(df){
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest_df[["data"]][[1]])
map(weather_nest_df[["data"]], weather_lm)
```

Keeping everything organized
1. Nest
2. Map
3. Function
```{r}
weather_nest_df %>%
  mutate(
    model = map(data, weather_lm)
  )
```

Unnesting
```{r}
weather_nest_df %>%
  unnest(data)
```

## Napolean Dyanmite!!

Here's my scraping function works for a single page

```{r}
read_page_reviews <- function(url) {
  url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

  dynamite_html = read_html(url)
  
  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>%
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )

  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```


What we did last time: 
```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_url <- str_c(base_url, c(1, 2, 4, 5))

read_page_reviews(vec_url[1])
read_page_reviews(vec_url[2])
read_page_reviews(vec_url[4])
read_page_reviews(vec_url[5])

dynamite_reviews <- 
  bind_rows(
  read_page_reviews(vec_url[1]),
  read_page_reviews(vec_url[2]),
  read_page_reviews(vec_url[3]),
  read_page_reviews(vec_url[4]),
  read_page_reviews(vec_url[5]),
)

map(vec_url, read_page_reviews)

napolean_reviews <-
  tibble(
    page = 1:10,
    page_url = str_c(base_url, page)
  ) %>%
  mutate(
    reviews = map(page_url, read_page_reviews)
  )

napolean_reviews %>%
  select(-page_url) %>%
  unnest(reviews)
```

WHY? Nesting and mapping helps make code more readable and concise


