---
title: "Writing Functions"
output:   
  github_document
---

If you use the same code more than twice, write a function!!!

1. Need to check inputs in function
2. Start small that does one thing well and interact easily - avoid unneeded complexity
3. Then add complexity (only if needed)

### Load packages
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)
```

## Z-Scores!

Let's compute the z-score version of a list of numbers.

```{r}
x_vec = rnorm(25, mean = 7, sd = 4)

(x_vec - mean(x_vec) / sd(x_vec))

```


Suppose you want to do this often.

```{r, error = FALSE}
z_scores = function(x){
  if(!is.numeric(x)){
    stop("Z scores only work for numbers")
  }
  
  if (length(x) < 3){
    stop("Z scores really only work if you have three or more numbers")
  }
  z = (x - mean(x) / sd(x))
  z
}
```

```{r, error = FALSE}
z_scores(x = x_vec)

z_scores(x = 1:10)
z_scores(x = rbinom(1000, 1, 0.6))

z_scores(x = 3)
z_scores(x = "My name is: ")
```

## Let's have multiple outputs

Let's just get the mean and sd from the vector input
```{r, error = FALSE}
mean_and_sd <- function(x){
  if(!is.numeric(x)){
    stop("Mean and SD only work for numbers")
  }
  
  if (length(x) < 3){
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}

mean_and_sd(x = x_vec)
mean_and_sd(x = 1:10)
mean_and_sd(x = rbinom(1000, 1, 0.5))
```


## Let's start with simulations...
```{r}
x_vec = rnorm(n = 25, mean = 7, sd = 4)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Can i do this using a function...
```{r}
sim_mean_sd <- function(n_obs, true_mean = 7, true_sd = 4){
  x = rnorm(n = n_obs, mean = true_mean, sd = true_sd)

  tibble(
    mean = mean(x),
    sd = sd(x)
  )
}

```

Does it work? Yes!
```{r}
sim_mean_sd(25, 100, 5)
```

## Scraping Amazon

original code
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```


Let's write a function to get reviews

```{r}
read_page_reviews <- function(url) {
  url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

  dynamite_html = read_html(url)
  
  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>%
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )

  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```

Let's try with URL

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

read_page_reviews(url)
```

What if I want multiple pages of reviews in 1 dataset?
```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_url <- str_c(base_url, c(1, 2, 4, 5))

read_page_reviews(vec_url[1])
read_page_reviews(vec_url[2])
read_page_reviews(vec_url[4])
read_page_reviews(vec_url[5])

dynamite_reviews <- 
  bind_rows(
  read_page_reviews(vec_url[1]),
  read_page_reviews(vec_url[2]),
  read_page_reviews(vec_url[3]),
  read_page_reviews(vec_url[4]),
  read_page_reviews(vec_url[5]),
)
```

Loading LOTR data

In the tidy data lecture, we broke the “only copy code twice” rule when we used the code below to process the LoTR words data:
```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = words, female:male) %>%
  mutate(race = str_to_lower(race)) %>% 
  select(movie, everything()) 
```

Maybe we can run a function on range and movie title
```{r}
lotr_load_and_tidy = function(path, range, movie_name) {
  
  df = readxl::read_excel(path, range = range) %>%
    janitor::clean_names() %>%
    gather(key = sex, value = words, female:male) %>%
    mutate(race = str_to_lower(race),
           movie = movie_name)
  
  df
  
}

lotr_tidy = 
  bind_rows(
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "B3:D6", "fellowship_ring"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "F3:H6", "two_towers"),
    lotr_load_and_tidy("./data/LotR_Words.xlsx", "J3:L6", "return_king")) %>%
  select(movie, everything()) 
```


## Functions as arguments

```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)
my_summary(x_vec, IQR)
my_summary(x_vec, var)
```


# Scoping and names
```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```

